% -*- fill-column: 110 -*-
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[margin=1in]{geometry}
% \usepackage{apacite}
\usepackage{color}
%\usepackage{sagetex}
\usepackage{fancyhdr}
\usepackage{setspace}
\pagestyle{fancy}
\lhead{\footnotesize Exercise Set 1.1}
\rhead{\footnotesize August 23 2013 -- MA325 -- Shae Erisson}

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\begin{document}

\section*{Exercise Set 1.1}
\begin{enumerate}
\item
  \begin{enumerate}
  \item Is there a real number $x$ such that $x^{2} = -1$?
  \item Does there exist a real number such that $x^{2} = -1$?
  \end{enumerate}

\item
  \begin{enumerate}
  \item Is there an integer $n$ such that $n$ has a remainder of 2
    when it is divided by 5 and a remainder of 3 when it is divided by 6?
  \item Does there exist an integer such that if $n$ is divided by 5
    the remainder is 2 and if $n$ is divided by 6 it has a remainder
    of 3?
  \end{enumerate}

\item 
  \begin{enumerate}
  \item Given any two real numbers $a$ and $b$, there is a real number
    $c$ such that $c$ is between $a$ and $b$.
  \item For any two real numbers, there is a real number $c$ such that
    $a < c < b$.
  \end{enumerate}

\item % question 4
  \begin{enumerate}
  \item Given any real number $r$, there is a real number $s$ such
    that $s$ is greater than $r$.
  \item For any real number $r$, there is a real number $s$ such that
    $s > r$.
  \end{enumerate}

\item % 5
  \begin{enumerate}
  \item Given any real number $r$, the reciprocal of $r$ is also positive.
  \item For any real number $r$, if $r$ is positive, then the
    reciprocal of $r$ is positive.
  \item If a real number $r$ is positive, then its reciprocal is positive.
  \end{enumerate}

\item % 6
  \begin{enumerate}
  \item Given any negative real number $s$, if $s$ is negative, the cube root of $s$ is negative.
  \item For any real number $s$, if $s$ is negative, then the cube
    root of $s$ is negative.
  \end{enumerate}

\item % 7
  \begin{enumerate}
  \item There are real numbers whose sum is less than their difference.
  \item There are real numbers that have a square less than their value.
  \item The square of a positive number is greater than the positive number.
  \item The absolute value of the sum of two numbers is always less
    than or equal to the sum of the absolute value of the two numbers.
  \end{enumerate}

\item % 8
  \begin{enumerate}
  \item All squares have four sides.
  \item Every square has four sides.
  \item If an object is a square, then it has four sides.
  \end{enumerate}


\end{enumerate}


\end{document}

% LocalWords: LocalWords differentiable
